% Cover letter using letter.cls
\documentclass{letter} % Uses 10pt
\usepackage{color}
\usepackage{amsmath}
\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8.5in    % text height can be bigger for a longer letter
\oddsidemargin=0pt   % leftmargin is 1 inch
\textwidth=6.5in     % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Kurt R. Rudolph}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{
Enova}

\begin{center}
{\large\bf Kurt R. Rudolph} 
\end{center}
\medskip\hrule height 1pt
\begin{center}
{11524 Fenwood Ct., Orland Park, IL 60467 \(\bullet\) \href{mailto:krudolph9@gmail.com}{krudolph9@gmail.com} \(\bullet\) (708) 620-7839 }
\end{center} \vfill % forces letterhead to top of page
 
\opening{To whom it may concern} 
 
\noindent I found Software Engineer position through the UIUC I-Link job board.
I graduated with my B.S. in Computer Science from UIUC in August 2012 
and have been doing freelance consulting work since.  I'm very 
passionate about programming and the possibilities of how computing 
may bring people together. Working largely alone though I've found 
my self rather isolated and have recently decided to pursue more 
collaborative career opportunities.
 
\noindent The Software Engineer position strikes me as particularly interesting for several reasons.  
Enova is a company where I can make a strong contribution.  I've worked with several companies 
over the past two years both successful and unsuccessful. While I am continually refining my understanding of what drives a business, the knowledge I currently hold likely will carry over well to Enova.
I believe I will get along well with the other engineers at Enova.
I am a passionate engineer, continually seeking new/unique challenges.  
And Enova is company were I believe I will grow tremendously and 
concur many new/unique challenges.


 
\noindent I look forward to the opportunity 
to speak with you further about my experience 
and interest in the Software Engineer position.
 
 
\closing{Sincerely,} 
 

 
%\encl{}					% Enclosures

\end{letter}
 

\end{document}
