% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion
\usepackage{hyperref}


\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Kurt R. Rudolph}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{508 E White \#12}
 \moveleft.5\hoffset\centerline{Champaign, IL 61820}
 \moveleft.5\hoffset\centerline{(708) 620-7839}


\begin{resume}
\section{OBJECTIVE} A passionate engineer who loves finding 
  solutions to problems. Currently pursuing entrepreneurial 
  aspirations building out Rudy Industries. Hopes success in 
  his career will enable him to continually face new and 
  unique challenges.
 

\section{EDUCATION} {\sl Computer Science}, College of Engineering  \\
                University of Illinois, Urbana-Champaign,
                August 2012 \\
 
\section{COMPUTER \\ SKILLS} 
  {\sl Programming Languages}: Ruby, C, CoffeeScript, C++, 
    Javascript, PHP, Bash, OCaml, MIPS Assembly, Python, Matlab, Java\\
  {\sl Markup Languages}: HTML, \LaTeX, Markdown, Haml, YAML, JSON\\
  {\sl Web Framworks \& Common Web APIs}: Ruby on Rails, Sinatra, NodeJS, jQuery,
    REST, Ajax, Backbone.js, Twitter-Bootstrap\\
  {\sl Version Control}: Git, Subversion, Mercurial\\
  {\sl Other Tools \& Notable Proficiencies}: Vim, Unix-Screen, 
    SSH, RVM, Able to manage and maintain most Unix \& Linux distributions 
    (most experienced with MacOS, FreeBSD, and Ubuntu), Able to navigate 
    Mac OS entirely via keyboard, experience interpolating 3D camera data 
    via CUDA C,
  
    
 
\section{EXPERIENCE} 
  {\sl Software Engineer \& Founder} \hfill Dec 2010 - Present \\
  Rudy Industries Inc, Pushing forward the horizon of tomorrow...
  \begin{itemize}  
    \itemsep -2pt %reduce space between items
    \item Founded during completion of undergrad to market computational
      services.
    \item Manage all financial and logistical aspects of the company.
    \item Have largely been contracted as full-stack developer. Most notably, 
      was one of 5 developers who built 
      \href{https://safelyfiled.com/home/}{SafelyFiled.com}.
    \end{itemize}
 
  {\sl Mentor} \hfill January 2013 - Present \\
    \href{Bloc}{https://www.bloc.io/}, Online Educational Institute 
     \begin{itemize}  
     \item Teaching students fundamental of programming, specifically those
        surrounding the Ruby on Rails web framework.
     \end{itemize} 
  {\sl Lab Aid} \hfill May 2011 - May 2012 \\
    University of Illinois, Urbana-Champaign, Department of Computer Science
      \begin{itemize}
        \itemsep -2pt %reduce space between items
        \item Organized resources for the Senior Projects courses
      \end{itemize} 
 
\section{COMMUNITY \\ SERVICE}  Organized and directed the 1988 and 1989 Grand 
                 Marshall Week \newline ``Basketball Marathon.'' A 24 hour 
                charity event to benefit the Troy Boys Club. Over 
                250 people participated each year. 

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            Elected {\it House Manager}, Rho Phi Sorority \\
            Elected {\it Sports Chairman} \\
            Attended Krannet Leadership Conference \\
                Headed delegation to Rho Phi Congress \\
                Junior varsity basketball team \\
                Participant, seven intramural athletic teams 
 

\end{resume}
\end{document}




