% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion
\usepackage{color}
\usepackage{amsmath}
\usepackage{hyperref}
\definecolor{dark-blue}{RGB}{0,60,125}
\hypersetup{
  colorlinks,
  citecolor=violet,
  linkcolor=red,
  urlcolor=dark-blue}
\renewcommand{\labelitemi}{{\tiny$\bullet$}}
%\renewcommand\labelitemi{}
%\addtolength{\voffset}{-10pt}
%\addtolength{\hoffset}{-20pt}



\begin{document}
% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Kurt R. Rudolph}
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{ 1753 W Augusta Blvd, Chicago, IL 60622 \(\bullet\) \href{mailto:krudolph9@gmail.com}{krudolph9@gmail.com} \(\bullet\) (708) 620-7839 }
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip


\begin{resume}
\small 
%\section{SUMMARY} A passionate engineer who loves finding 
%  solutions to problems. Hopes success in 
%  his career will enable him to continually face new and 
%  unique challenges.
\section{EDUCATION} {\bf University of Illinois } \hfill Urbana-Champaign, IL\\
                    {\sl Bachelor of Science in Computer Science \hfill August 2012 \\
                    Focus: Database Systems \& Mathematics \hfill GPA: 2.56/4.00\\}

%            \begin{ncolumn}{2}
%              {\scriptsize Database Systems }&{\scriptsize Graph Theory }\\
%              {\scriptsize Data Mining }&{\scriptsize Linear Algebra }\\
%              {\scriptsize Interactive Computer Graphics  }&{\scriptsize Differential Equations }\\
%              {\scriptsize Programming Languages and Compilers }&{\scriptsize Probability Theory }\\
%              {\scriptsize Operating Systems Design }&{\scriptsize Numerical Methods I \& II }\\
%              {\scriptsize Senior Project I \& II }&{\scriptsize Computational Theroy }\\
%              {\scriptsize Undergraduate Research Laboratory }&{\scriptsize Fundamental Algorithms }\\
%            \end{ncolumn}
 
\vspace{-2mm}
\section{ WORK EXPERIENCE} 
  {\bf \href{http://www.erisfutures.com/}{Eris Exchange}}\\
  {\sl Software Engineer} \hfill November 2013 - Present
\vspace{-5mm}
  \begin{itemize}
    \itemsep -2pt %reduce space between items
    \item Support financial exchange build on a \href{http://www.rabbitmq.com/}{RabbitMQ} core (an \href{http://www.erlang.org/}{Erlang} library) and Ruby on Rails back end built on JRuby.
    \item Coordinate with control center to improve product usability and reliability.
    \item Rearchitected system to support trade void functionality.
    \item Made performance improvements to adapter connecting to business partner.
    \item Rebuilt several components using "Eris Application" framework.
    \item Built out generalized clone feature and applied to clearing firms and users accounts.
    \item Identified and fixed security vulnerabilities.
    \item Built out more granular user permissions to product types.
    \item Many bug fixes: first fixing rate calculation, UI tweaks, holiday run issues.
  \end{itemize}

  {\bf Rudy Computing}
  {\sl Software Engineer \& Founder} \hfill August 2012 - November 2013
  
\vspace{-5mm}
  \begin{itemize}
    \itemsep -2pt %reduce space between items
    \item Contracted as full stack developer for implementation of LAMP based web app \href{https://safelyfiled.com/home/}{SafelyFiled.com} for the duration of four months.
    \item Implemented Java based mail monitoring/alert software for \href{http://www.boldwebservices.com/}{Bold Web Services}.
    \item Wrote \href{http://rudycomputing.github.io/shopsense-ruby/}{shopsense-ruby} gem.
    \item Built single page \href{http://pure-refuge-1784.herokuapp.com/}{administration panel} using backone.js.
    \item Building off the Linux based RaspberryPi board and working closely with data acquisition hardware designers, developed software to aggregate and analyse the data of the sensory devices for \href{https://github.com/RudyComputing/CombustionEmissionsTesting}{combustion emissions testing devices}.  Contracted by the University of Illinois, Department of Environmental Engineering.
    \item Wrote \href{https://github.com/RudyComputing/microAeth-AE51-Ruby}{microAeth-AE51-ruby} gem.
    \item Built Amazon Marketplace Web Service reporting application building off Rails.
  \end{itemize}
\section{PROJECT EXPERIENCE}
\vspace{-1mm}
  \begin{itemize}
    \item \href{https://github.com/KurtRudolph/CudaMP/raw/master/Paper/CS493-RockwellCollins-FinalPaper.pdf}{CudaMP} - A Message Passing Interface (MPI)-like protocol for Graphics Processing Units (GPUs) developed by my senior project team. The video is the application of the project performing the rasterization of the 3d-view OpenKinect project yielding slightly faster results than OpenGL.
    \item \href{http://kurtrudolph.net/2012/10/11/alternative-high-performance-benchmarks/}{Alternative High Performance Benchmarks} - A project featured in the PGAS section of 2011 Supper Computing conference.  The project explores PGAS languages for alternative HPC benchmarks, specifically a UPC implementation of the Graph 500.
  \end{itemize}

\section{COMPUTER \\ SKILLS} 
\begin{tabular}{*{1}{p{3.6cm}p{8.6cm}}}
    {\sl Programming Languages}: & {\footnotesize Proficient: Ruby, Javascript, C; familiar: C++, MIPS, Erlang, Python, Coffeescript}.\\
    {\sl Markup Languages}: & {\footnotesize HTML, \LaTeX, Markdown, Haml, YAML, JSON}.\\
    {\sl Web Frameworks \& Common WebAPIs}: &
      {\footnotesize Ruby on Rails, Knockout.js, Sinatra, Apache, jQuery, 
      REST, Ajax, Backbone.js, Twitter-Bootstrap}.\\
    {\sl Other Tools \& Notable Proficiencies}: &
      {\footnotesize MongoDB, Git, Vim, CUDA, OpenGL, Subversion, Unix-Screen,
      SSH, able to administrate most Unix \& Linux distributions, navigate
      Mac OS \emph{entirely} via keyboard, SQL (MySQL \& PostgreSQL)}.\\
\end{tabular}


\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
  \begin{itemize}
      \itemsep -2pt %reduce space between items
      \item Attend \href{http://opengovhacknight.org/}{Chicago Open Gov Hack Night}, \href{http://www.meetup.com/Chicago-C-CPP-Users-Group/}{C/C++ Users Group}, 
    \item Completion of \href{http://www.vscse.org/summerschool/2012/manycore.html}
          {VSCSE Proven Algorithmic Techniques for Many-core Processors}.
    \item Active participant of \href{http://stackoverflow.com/users/1134742/rudolph9}{StackOverflow}.
    \item Awarded 1st prize at the \href{http://lincolnlabs.com/hackathons/chicago.html}{2013 LincolnLabs Chicago Hackathon} for Chi-Text.
    \item Personal website, \href{http://kurtrudolph.net/about}{KurtRudolph.net} (please see site more extra-curricular activities).
  \end{itemize}
\end{resume}
\end{document}
